---
title: "changing-parameter-for-multiple-reports"
format: html
editor: visual
params:
  species: setosa
---

```{r}
#| warning: false
library(dplyr)
library(ggplot2)
```

Iris data set has 3 species:

```{r}
unique(iris$Species)

```

To create a separate report for each species, define the `params` in the YAML section at the top of the qmd file. Let's try with setosa.


```{r eval=FALSE} 
---
title: "changing-parameter-for-multiple-reports"
format: html
editor: visual
params:
  species: setosa
---
```

Create a function whose input is a species' name and output is a plot for that species.

```{r}
report <- function(species){
  
  iris %>% filter(Species == species) %>% 
  ggplot(aes(Petal.Length, Petal.Width)) +
  geom_point() +
  theme_minimal() +
  
  labs(title = paste0("Report on ", species))
}
```

Call the function and referring to the parameter. 

```{r}
report(params$species)
```

Cross-reference to the species that is specify in the parameter in YAML section.


```{r eval=FALSE}
The plot displays the relationship between petal length and petal 
with in `r params$species` species.
```

The plot displays the relationship between petal length and petal with in `r params$species` species.


To produce a report for another species, say `virginica`, all we need to do is to change `params` in the YAML: 

```{r eval=FALSE} 
---
title: "changing-parameter-for-multiple-reports"
format: html
editor: visual
params:
  species: virginica
---
```
